An Agent-based Model of Interdisciplinary Interactions\\\medskip \textit{Ecole thématique de Rochebrune 2018\\ Proposition de Communication }

### 2019-02-13 Docs/Rochebrune2018/rochebrune.tex
data_cited

@@

>>>>

Akerlof, G. A., & Michaillat, P. (2018). Persistence of false paradigms in low-power sciences. Proceedings of the National Academy of Sciences, 201816454.

@@

http://bingweb.binghamton.edu/~sayama/NSF-SoO/ abm for group orga

Pluchino, A., Biondo, A. E., & Rapisarda, A. (2018). Talent Versus Luck: The Role Of Randomness In Success And Failure. Advances in Complex Systems, 21(03n04), 1850014.

Twin-Win Model: A human-centered approach to research success

Modeling research universities: Predicting probable futures of public vs. private and large vs. small research universities
